Coherent optical association of single molecules

### 2020-08-04 paper.tex
figure

>>>>

% Introduction

Trapped neutral molecules, assembled in an array of optical tweezers,
are a promising platform to study quantum infoqrmation and quantum simulations.

\begin{figure*}
  \includegraphics[height=4.5cm]{fig1.pdf}
  \caption{Optical creation of single molecule from single atoms in tweezer.
    (A) Schematics of the Raman transition. \todo{more about the states involved}
    (B) Geometry and polarization of trap and Raman beam relative to the bias magnetic field.
    \todo{Field strength, power, polarization description (pi)}
    (C) Molecule formation pulse sequence. The tweezer initially consists of only up leg power.
    This power is smoothly ramped down and the down leg power ramped up over $10\mu s$ while
    maintaining the total power of the tweezer.
    \todo{to minimize heating?}
    \label{f-setup}
  }
\end{figure*}

\begin{figure*}
  \includegraphics[height=4.5cm]{fig2.pdf}
  \caption{
    (A) Raman resonance from atomic state to molecular state, showing Fourier limited linewidth.
    \todo{states, time}
    (B) Rabi oscillation on resonance
    \label{f-raman}}
\end{figure*}

\begin{figure*}
  \includegraphics[height=4.5cm]{fig3.pdf}
  \caption{
    (A) Molecule lifetime in 15 mW of trap depth \todo{lifetime number}
    (B) Two-body atom lifetime in 15 mW of trap depth \todo{lifetime number,
      subtraction of single body, photoassociation rate}
    \label{f-lifetime}}
\end{figure*}

% In this Letter, we demostrate that a single ground state molecule can be formed
